Union and intersection contracts are hard, actually

### 2021-06-09 paper.tex
Wibbles

In return, the complexity is offloaded to a separate procedure that must decide
when to raise blame. This complexity is salient in the deterministic, sequential
version\footnote{cf Section 5.1 of \cite{KeilThiemannUnionIntersection}}. There,
the evaluation procedure has to deal again with the problem of eliding contracts
that are not \emph{compatible}\footnote{You can check more on this topic on
Section 5.1 of \cite{KeilThiemannUnionIntersection}} (contracts are incompatible
if they are coming from a different branch and should be ignored). In practice,
the evaluation procedure maintains a global environment of contracts that is
extended each time a non-trivial contract (union, intersection or higher-order)
is opened. Then, any contract application must check the presence of the
corresponding label in the environment. What's more, each time a function with a contract attached is applied,
the whole \emph{context} (that is, the continuation of the application) must be
must be checked for compatibility with respect to each label of the contract
environment. Checking for compatibility involves searching the context for
contract applications.

>>>>

In return, the complexity is offloaded to a separate procedure that must decide
when to raise blame. This complexity is salient in the deterministic, sequential
version~\cite[Section 5.1]{KeilThiemannUnionIntersection}. There,
the evaluation procedure has to deal again with the problem of eliding contracts
that are not \emph{compatible}~\cite[Section 5.1]{KeilThiemannUnionIntersection} (contracts are incompatible
if they are coming from a different branch and should be ignored). In practice,
the evaluation procedure maintains a global environment of contracts that is
extended each time a non-trivial contract (union, intersection or higher-order)
is opened. Then, any contract application must check the presence of the
corresponding label in the environment. What's more, each time a function with a contract attached is applied,
the whole \emph{context} (that is, the continuation of the application) must be
must be checked for compatibility with respect to each label of the contract
environment. Checking for compatibility involves searching the context for
contract applications.
